Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-07-24 ms.tex
added some RPI vs RPF time series

\begin{figure*}
{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.49\textwidth}{Stripe Mode TIme Series}
\fig{azlab_ratio_tser_window.pdf}{0.49\textwidth}{Window Mode Time series}}}
\caption{Stripe mode (4 output amplifiers) gives better precision than window mode (one amplifier).}\label{fig:stripeVsWindowAZlab04}
\end{figure*}

@@

>>>>

\begin{figure*}
{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.49\textwidth}{Stripe Mode Time Series}
\fig{azlab_ratio_tser_window.pdf}{0.49\textwidth}{Window Mode Time series}}}
\caption{Stripe mode (4 output amplifiers) gives better precision than window mode (one amplifier).}\label{fig:stripeVsWindowAZlab04}
\end{figure*}

@@

\begin{figure*}
{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.33\textwidth}{Reset-per-frame, 2048x256}
\fig{azlab_ratio_tser_RPI.pdf}{0.33\textwidth}{Reset-per-integration, 2048x256}}}
{\gridline{\fig{azlab_ratio_tser_stripe64_1p5_mA_rpt2.pdf}{0.33\textwidth}{Reset-per-frame, 2048x64}
\fig{azlab_ratio_tser_stripe64_1p5_mA_rpt3rpi.pdf}{0.33\textwidth}{Reset-per-integration, 2048x64}}}
\caption{Reset per integration versus reset per frame.}\label{fig:subarraySizes}
\end{figure*}
